Non-convergence in iterative imputation

### 2022-06-13 Manuscript/Manuscript.Rmd
Visualize simulation results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(purrr)
library(mice)
miceadds::source.all("R")
```

@@

```{r eval=FALSE, include=FALSE}
dat <- generation()
amp <- amputation(dat)
imp <- imputation(amp)
est <- evaluation(imp)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# filters
coeff <- "X4"
maxit <- 20
```

```{r data}
performance <- readRDS("./Results/performance.RDS")
summary <- performance %>% 
  group_by(method, mech, prop, .it, term) %>% 
  summarise(across(c(bias, cov, ciw, ac, psrf), mean, na.rm = TRUE))
SEs <- performance %>% 
  group_by(method, mech, prop, .it, term) %>% 
  summarise(across(c(bias, ciw, ac, psrf), var, na.rm = TRUE)) %>% 
  mutate(across(c(bias, ciw, ac, psrf), sqrt))
results <- left_join(summary, SEs, by = c("method", "mech", "prop", ".it", "term"), suffix = c("", "_SE")) %>% 
  mutate(cov = cov,
         cov_SE = sqrt((cov * (1 - cov)) / 2000))
```

@@

@@

```{r}
# results %>% 
#   filter(term == "X2", .it < 26) %>% 
#   ggplot(aes(x = .it, y = bias)) +
#   geom_hline(yintercept = 0, color = "grey", size = 2) +
#   geom_line(color = "blue") +
#   geom_line(aes(x = .it, y = bias + bias_SE), color = "lightblue", linetype = "dashed") +
#   geom_line(aes(x = .it, y = bias - bias_SE), color = "lightblue", linetype = "dashed") +
#   facet_grid(as.factor(prop) ~ mech) +
#   theme_classic()

results %>% 
  filter(term == coeff, .it > 0, .it < maxit + 1) %>% 
  ggplot(aes(x = .it, y = bias)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_errorbar(aes(ymin = bias - bias_SE, ymax = bias + bias_SE), alpha = 0.1) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  facet_grid(as.factor(prop) ~ mech) +
  theme_classic()

results %>% 
  filter(term == coeff, .it > 0, .it < maxit + 1) %>% 
  ggplot(aes(x = .it, y = ac)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_errorbar(aes(ymin = ac - ac_SE, ymax = ac + ac_SE), alpha = 0.1) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  facet_grid(as.factor(prop) ~ mech) +
  theme_classic()

results %>% 
  filter(term == coeff, .it > 0, .it < maxit + 1) %>% 
  ggplot(aes(x = .it, y = psrf)) +
  geom_hline(yintercept = 1, color = "black") +
  geom_errorbar(aes(ymin = psrf - psrf_SE, ymax = psrf + psrf_SE), alpha = 0.1) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  facet_grid(as.factor(prop) ~ mech) +
  theme_classic()
```
